---
title: "lendops - Monthly Operations Report"
format: 
  html:
    theme: flatly
    toc: true
execute:
  echo: false
  message: false
  warning: false
params:
  month: "Latest"
---

```{r setup}
library(ggplot2)
library(scales)
library(dplyr)
library(targets)
library(knitr)

# Load data from the targets pipeline cache
kpi_data <- tar_read(kpi_data)
decline_reasons <- tar_read(decline_reasons)
tat_data <- tar_read(tat_data)
```

# Executive Summary

::: {.callout-note appearance="simple"}
**Reporting Period:** `r params$month` | **Status:** Automated via `{targets}` pipeline
:::

This report provides an automated overview of the Credit-SME origination funnel and portfolio health. 

During this period, the department processed **`r format(kpi_data$total_applications, big.mark = ",")`** applications, resulting in an approval rate of **`r percent(kpi_data$approval_rate, accuracy = 0.1)`**. Total disbursement volume stood at **BDT `r format(round(kpi_data$total_disbursed_amt / 10000000, 1), nsmall = 1)` Cr**, with an average ticket size of **BDT `r format(round(kpi_data$avg_ticket_size / 100000, 1), nsmall = 1)` Lakh**.

## Decline Breakdown

Of the `r format(kpi_data$total_applications - kpi_data$disbursed_loans, big.mark = ",")` applications not disbursed, the primary drivers were:

```{r decline-table}
decline_reasons |>
  dplyr::mutate(percentage = count / sum(count)) |>
  knitr::kable(col.names = c("Decline Reason", "Count", "Percentage"),
               format.args = list(big.mark = ","), 
               digits = 2) # kable formats numeric to 2 decimals by default for percentage
```

# Origination Turnaround Time (TAT)

The chart below highlights the average processing time (in hours) for applications across different branches and stages. The SLA threshold for stage processing is 48 hours.

```{r tat-chart, fig.width=10, fig.height=5}
if (nrow(tat_data) > 0) {
  # Highlight Documentation stage in red to make the bottleneck stand out
  tat_data <- tat_data |>
    mutate(stage_color = ifelse(stage == "Documentation", "Documentation", "Other Stages"))
  
  ggplot(tat_data, aes(x = branch, y = avg_tat_hours, fill = stage_color)) +
    geom_col(position = "dodge") +
    geom_hline(yintercept = 48, linetype = "dashed", color = "red", linewidth = 1) +
    annotate("text", x = 1, y = 52, label = "SLA (48h)", color = "red", hjust = 0) +
    labs(x = NULL, y = "Avg TAT (Hours)", fill = "Stage") +
    scale_fill_manual(values = c("Documentation" = "#d9534f", "Other Stages" = "#5bc0de")) +
    theme_minimal() +
    theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1))
}
```

::: {.callout-warning}
**Key Insight - Process Bottleneck:** 
The **Gulshan** and **Dhanmondi** branches are exhibiting severe bottlenecks in the **Documentation** stage, with processing times breaching the 48-hour SLA by 2x (averaging ~80 hours). Immediate operational review is recommended for these branches.
:::